Baseline centering problem

### 2018-12-19 paper/tangotd.tex

I still don't know how to rightly combine these three equations.

>>>>

I still don't know how to rightly combine these three equations. I'm not
even sure this kernel/image thing is actually an issue: if $f$ and
$\green$ are represented as neural networks with some input features,
the kernel of $f$ is actually the set of functions/distributions on
states which have the same average features, and the image of
$\transp{\green}$ is the set of functions that can be represented as sums
$V(s)=\sum_i \alpha_i\green_i(s)$ over the components of $\green$: if $V$
indeed belongs to this class then we will compute it correctly. (But this
class does not change during training...)
